%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Software Developer{\enskip\cdotp\enskip}golang} % Job title
    {Acronis, Inc.} % Organization
    {Sofia, Bulgaria} % Location
    {May. 2021 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing integrations}
        \item {golang, PostgreSQL}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Developer{\enskip\cdotp\enskip}golang} % Job title
    {Regemini, Inc.} % Organization
    {California, USA} % Location
    {May. 2020 - May. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing web scrapping services}
        \item {golang, ELK, Kafka, Mongo}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer{\enskip\cdotp\enskip}golang} % Job title
    {Technology, LLC.} % Organization
    {Naberejnie Chelny, Russia} % Location
    {Oct. 2019 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing api testing tool.}
        \item {golang, PostgreSQL, MSSQL, SOAP}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer{\enskip\cdotp\enskip}golang} % Job title
    {Zirra.co Ltd} % Organization
    {Tel Aviv, Israil (Remote)} % Location
    {Apr. 2018 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Programming of data systems that extract information from many sources, then process, then normalize, and analyze the information that powers Zirra products.}
        \item {Adding new data sources, expanding existing data processing capabilities and integrating new models and analytics.}
        \item {Processing structured and unstructured data to produce trading signals and indicators.}
        \item {Increase data quality using AWS MTurk in order to increase data quality.}
        \item {mongoDB, PostgreSQL (pgx), docker, aws mturk, HTML parsing(goquery), rest API (go-restful), unit tests}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Lead/Frontend Developer} % Job title
    {Realty Cloud - selling e-signed authority document about asset owners} % Organization
    {Naberejnie Chelny, Russia} % Location
    {Dec. 2017 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {SaltStack, gitlab CI, nomad, golang, typescript angular 6, PostgreSQL}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CTO} % Job title
    {TruckMove - transport management system} % Organization
    {Naberejnie Chelny, Russia} % Location
    {2015 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {SaltStack, gitlab CI, nomad, consul, golang, typescript angular 6, PostgreSQL, EGTS, Asterisk, microservices (go-micro), GPRC}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
